---
title: "day4-interactivities"
format: html
editor: visual
execute: 
  warning: false
---

## Functions

Make a function that doubles a value.

```{r}
double_value <- function(my_dollars){
  print(2*my_dollars)
}
```

```{r}
double_value(my_dollars = 10.3)
```

```{r}
monthly_income <- c(42.50, 61, 75, 89.50)


```

Create a function that returns an awesome restaurant name given a cool animal and your favorite good.

```{r}
name_restaurant <- function(animal,food) {
  print (paste0(animal,food))
}

name_restaurant(anima = "hawk", food = "pizza")
```

Given temperature in degrees Fahrenheit, write a function that converts it to Celsius.

```{r}
convert_f_to_c <- function (temp_f) {
  temp_c = 5/9 * (temp_f-32)
  return (temp_c)
}
```

```{r}
convert_f_to_c (52)
```

Create a function that given inputs of age and hometown, returns "I am \_\_\_ years old, and I'm from \_\_\_\_"

```{r}
personal_info <- function (age, birth_country) {
  print (paste("I am", age, "years old, and I'm from",birth_country,"."))
}
```

```{r}
personal_info(1,"north pole")
```

```{r}
double_value2 <- function(dollars) {
  dollars*2
}
```

```{r}
double_value2(dollars = 10)
```

Print statements and return statements

Print: "show me ", Return: "store this so I can use it later"

## Functions with conditionals

```{r}
calculate_anmial_age <- function(species,age_human_years){
  if (species == "dog") {
    age_human_years * 7
  } else if (species == "goat") {
    age_human_years * 4.7
  } else {
    print("Please enter dog or goat.")
  }
}
```

```{r}
calculate_anmial_age(species = "dog", age_human_years = 10)

calculate_anmial_age(species = "goat", age_human_years = 4)

calculate_anmial_age(species = "whale", age_human_years = 8) # no shows at all 
```

Write a function that, given temperature in Kelvin, if a user selects "metric" to the scale then return degrees Celsius, or if they select "english" then return degrees in Fahrenheit.

```{r}
temp <- function (user, kelvin) {
  if (user == "metric") {
     kelvin - 273.15
  } else if (user == "english") {
     (kelvin-273.15)*1.8 +32
  }
}
```

```{r}
temp("english",232)
```
